Puyuma: Linux-based RTOS experimental platform for constructing self-driving miniature vehicles

### 2017-05-14 cthpc-2017/paper.tex
Add lane detector work condition
Add lane following working flow
Refer article to duckietown

We created an artificial environment that the lane detector can be implemented easier. The lane detector detects segments from image, and identifies the lane by using several computer vision techniques like Canny edge detection, HSV color thresholding      and Hough transform.

@@

@@

>>>>

We refer to MIT Duckietown's experience \cite{Duckietown} and created an artificial environment that the lane detector can be implemented easier. The lane detector detects segments from image, and identifies the lane by using several computer vision techniques like Canny edge detection, HSV color thresholding and Hough transform.

@@

\begin{figure}
	\centering
	\includegraphics[width=3in]{img/lane_flow.png}
	\caption{lane following algorithm work flow}
	\label{fig:lane_following_flow}
\end{figure}

@@

\subsubsection{Lane detector work conditions}
$ $
\begin{table}[!htbp]
	\centering
	\caption{Lane detector work conditions}
	\label{lane_detector_condition}
	\begin{tabular}{ll}
		Frame rate                      &10fps \\
		Image format                    &8-bits RGB cv::Mat \\
		Image size                      &320x240 px	 \\	
		ROI (Region of Interest) size   &320x120 px
	\end{tabular}
\end{table}
